Isomorphic Interpreters from Logically Reversible Abstract Machines

### 2012-03-22 iso-int/rc-iso-int.tex

\begin{center}
\scalebox{0.85}{
  \includegraphics{diagrams/pi0-2.pdf}
}
\end{center}

@@

We have developed a technique for the systematic development of
{{langRevT}} programs from logically reversible small-step abstract
machines. Since techniques for developing small-step interpreters are
well developed this allows for the direct development of a large class
of {{langRevT}} programs. We have demonstrated the effectiveness of
this approach by deriving meta-circular interpreter for {{langRevT}}
in this style.

>>>>

\begin{center}
\scalebox{0.9}{
  \includegraphics{diagrams/pi0-2.pdf}
}
\end{center}

@@

We have developed a technique for the systematic derivation of
{{langRevT}} programs from logically reversible small-step abstract
machines. Since techniques for devising small-step interpreters are
well known, this allows for the direct development of a large class of
{{langRevT}} programs.  We have demonstrated the effectiveness of this
approach by deriving a meta-circular interpreter for {{langRevT}}.
